### 2025-10-17 REVIEWER_RESPONSE_ORGANIZED.md

### B. **Ancestry Stratification** (Reviewer #3)
- [ ] Stratify prediction performance by genetic ancestry
- [ ] Compare model performance across EUR, AFR, EAS, SAS populations
- [ ] Show signature consistency across ancestries
- **Status**: Have PRS file with ancestry PCs (ukb.kgp_projected.tsv)

### C. **Selection Bias Analysis** (Reviewer #1, #3)
- [ ] Apply inverse probability weighting (IPW)
- [ ] Email tabea.schoeler@unil.ch for IPW weights
- [ ] Show cohort TDI distribution vs. general population
- [ ] Compare results with/without IPW
- **Status**: Alternative - show distribution comparisons across biobanks

### D. **Clinical Comparisons** (Reviewer #1)
- [ ] Direct AUC comparisons with PCE, PREVENT, GAIL
- [ ] Add PRS baseline models
- [ ] Three-way comparison: Clinical vs. PRS vs. Aladynoulli
- **Status**: Have clinical scores, need to run formal comparisons

* points to signautres to explain the processes, intuitive physiological
** transitions: metabolic to cardiovascular, inflammatory to cancer,

* what icds are contributing to the example, rich and complicated, perfectly transparent
* exactly what it is that is going the perfectly transparent, the generative model, the parameters, the signatures

** ways to automatically create a dumbed down version 
   * for example it is easy to create
